### 2019-05-17 doc/bilevel/paper.tex
Updates to include a new pyomo example for bilevel

\begin{qlisting}
from pyomo.environ import *
import pyomo.kernel as pmo
from pao.bilevel import *
model = ConcreteModel()
model.x = Var(bounds=(1,2))
model.v = Var(bounds=(1,2))
model.y = Var(bounds=(1,2))
model.w = Var(bounds=(-1,1))
model.upper = SubModel(vars=[model.x,model.v])
model.lower = SubModel(vars = [model.y,model.w], parent = upper, 
		type = optimistic, argmin = model.y)

>>>>

\begin{qlisting}
from pyomo.environ import *
from pao.bilevel import *
model = ConcreteModel()
model.x = Var(bounds=(1,2))
model.v = Var(bounds=(1,2))
model.y = Var(bounds=(1,2))
model.w = Var(bounds=(-1,1))
model.upper = SubModel(vars=[model.x,model.v])
model.lower = SubModel(vars = [model.y,model.w], parent = upper, 
		type = optimistic, argmin = model.y)
